%% Copyright 2022 Kiril Urivsky.
% https://github.com/kiril-u/kiril-resume-2022
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


% -------------------------- MODERNCV ---------------------------
% \documentclass[11pt,a4paper,roman]{moderncv}      % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
% \moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'

% \moderncvcolor{blue} % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
% \nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
% \usepackage[utf8]{inputenc}
% \usepackage{fontawesome}
% \usepackage{tabularx}
% \usepackage{ragged2e}

%% !!!!!!!!!!!!!!!!!!!!!!
% adjust the page margins
% \usepackage[scale=0.8]{geometry}
% \usepackage{multicol}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
% \usepackage{enumitem}
% \setlist[description]{leftmargin=1cm,labelindent=1cm}
% \usepackage{import}

% -------------------------- MODERNCV ---------------------------
\documentclass[]{rahulworld-resume}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{anyfontsize}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\begin{large}
	\headername{Kiril Urivsky}\\
\end{large}

Brief self description in a few words
\vspace{8pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Contact Info} 

\href{mailto:kirilurivsky@gmail.com}{kirilurivsky@gmail.com} \\
\href{tel:972525470608}{052-547-0608} \\
\href{https://www.linkedin.com/in/kiril-u}{linkedin.com/kiril-u} \\
\href{https://goo.gl/maps/MSacjpSy7vZSKykP7}{Ashdod} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Languages \& Technology
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Languages \& Technology} 
%\noindent\rule{5cm}{0.4pt}\\
%\datecolor{20XX-20YY}
\subsection{Languages}
\textbf{English, Hebrew, Russian}.\\
Highly proficient and well-versed in the syntax, grammar and pragmatic use of all three in causal, organizational, and academic discourse.
\vspace{2pt}
%\datecolor{20XX-20YY}
\subsection{Computer Languages}
% \begin{enumerate}[leftmargin=0.75cm,label=\textcolor{cyan}{\textbullet}]
\textbf{Interpretive languages:} \\
Bash, Bourne Shell, and other similar POSIX-compliant languages. 

\textbf{Markup languages:} \\
Markdown, HTML, XML, and LaTeX.
% \textbf{Programming languages} \\
% Superficial knowledge of C, Java and JavaScript. \\
\vspace{2pt}
\subsection{Software}

Microsoft Office: Word, PowerPoint, Excel, Outlook, OneNote, Publisher, and Access. 

Statistics: IBM's SPSS, AMOS, and JASP. 

Editing: Adobe Photoshop, GIMP, Krita; Sony Vegas, Kdenlive. 
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Certifications}
%\noindent\rule{5cm}{0.4pt}
\datecolor{2009--2010}
Computer Technician Course
\href{https://loona-il.000webhostapp.com/resume-references/computer-technitian-certificate.jpg}{IQline, Academy of Sciences and Arts}\\

Installation and maintenance of computer operating systems (Windows, GNU/Linux), providing technical support, troubleshooting, and repair of hardware components and peripheral equipment.

%	\begin{enumerate}[leftmargin=0.75cm,label=\textcolor{cyan}{\textbullet}]
%		\itemsep 0em 
%		%\begin{itemize}
%		\item Installation and maintenance of computer operating systems (Windows, GNU/Linux), hardware, and software packages.
%		\item Setup and management of local area network infrastructures.
%		\item Providing technical support, troubleshooting, and repair of hardware components and peripheral equipment. 
%		%\end{itemize}
%	\end{enumerate}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Community Involvement
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Community Involvement}
% \noindent\rule{5cm}{0.4pt}
\datecolor{2017--2018}
Mental Health Assistant at Clalit's Mental Health Clinic, Eilat. \\
Assisted physicians, health practitioners, and psychiatrists in working with patients with mental or emotional disorders. \\
\datecolor{2015--2018}
Mentorship at Perach \\
Acted as a tutor and mentor for underprivileged children
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Military Service
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Military Service}
\datecolor{2013--2014}
NCO of Casualty Assistance at IDF's Combat Engineering Corps
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
% \descript{BS in Computer ence}
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\
%\hspace*{0pt}\hfill J-90, NIT Srinagar, Hazaratbal \\
%\hspace*{0pt}\hfill Srinagar, J$\&$ K-190 006, India \\
%\hspace*{0pt}\hfill Mob.: +91-8449368522 \\
%\hspace*{0pt}\hfill Email.:\textbf{\href{mailto:rahulnitsxr@gmail.com}{rahulnitsxr@gmail.com}} \\
%\hspace*{0pt}\hfill Web.:\textbf{\href{http://rahulchauhan.net}{http://rahulchauhan.net}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{2019--2021} \runsubsection{Educational Psychology, Max Stern Yezreel Valley College.}
\descript{Master of Arts}
\noindent
\hspace{5em}%
\begin{minipage}{0.90\textwidth\vspace{2pt}}
Conducted evaluations for students to determine their eligibility for special needs programs.

Worked with teachers to develop and help implement classroom management procedures and Individualized Educational Programs for at-risk students. 

Coordinated with teachers and administrative staffs to implement academic programs based on student’s potential.

Provided counseling services to parents on behavior management techniques and parenting skills.
\end{minipage}
% \descriptright{Python, PostgreSQL, Pandas, Numpy, Scipy, Pint, Postgresql-unit, Javascript}
\sectionsep

\datecolor{2015-2018} \runsubsection{\href{https://loona-il.000webhostapp.com/resume-references/BA-and-honorary.pdf}{{\fontsize{11}{11}\selectfont Psychology and Multidisciplinary Studies.} {\fontsize{10}{10}\selectfont Ben-Gurion University}}}
\descript{\href{https://loona-il.000webhostapp.com/resume-references/BA-and-honorary.pdf}{\fontsize{11}{11}\selectfont Bachelor of Arts, Summa Cum Laude, 95.00}}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
	\datecolor{2018}
	\href{https://loona-il.000webhostapp.com/resume-references/BA-and-honorary.pdf}{Received Rector's Award for outstanding academic achievement} \\
	\datecolor{2017}
	\href{https://loona-il.000webhostapp.com/resume-references/BA-and-honorary.pdf}{Received Department Chair’s Excellency Award}
\end{minipage}
% \descriptright{ExtJS, Dygraph.js, D3.js, Data analysis, Python, PostGIS, Pandas, Numpy, Scipy}
\sectionsep

\datecolor{20XX-now} \runsubsection{Indian Institute of Science, Banglore}
\descript{Research Intern}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
pan sharpening is one kind of data fusion become very wide spread method which populate the spectral band information with the influence of high spatial information.
\end{minipage}
\descriptright{Satellite images(Chandrayan), Fusion Algorithm, Java}
\sectionsep

\datecolor{20XX-now} \runsubsection{Smokey, Banglore}
\descript{Android Intern}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Worked on location based services application which provide services at any location near
services provider and also made friend module.
\end{minipage}
\descriptright{Android, Mysql, Google map}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements/Awards} 
\noindent\rule{12.5cm}{0.4pt}
\datecolor{20XX-now} \runsubsection{Rajsthan Hackathon}
\descript{Participated}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
In this hackathon Developed distributed Voting Application.
\end{minipage}
\datecolor{20XX-now} \runsubsection{Angelhack, Jaipur}
\descript{Finalist}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
In this hackathon Developed a Dapp using Blockchain which is based on smart contract.
\end{minipage}
\datecolor{20XX-now} \runsubsection{Digital India}
\descript{Grand Prize Winner}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
In this hackathon developed a web-app in which showing kashmir as paradise on earth.
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SIDE PROJECT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Side Project}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{20XX-now} \runsubsection{Digital Certificate Dapp using Ethereum}
\descript{Blockchain, Web3JS}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
A Dapp issue certificate and verify. An Idea to use Blockchain to create Digital Certificate.
\end{minipage}
\datecolor{20XX-now} \runsubsection{Identifying Gender From Images of Faces}
\descript{ML}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Identifying gender of a person by looking at his/her Photograph.
\end{minipage}
\datecolor{20XX-now} \runsubsection{Small Project}
\descript{Android, Data Analysis, Image Processing}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Result Portal, Voice Calci, Cubic Bispline, Image Compression, smoothing, Fitting Curve.
\end{minipage}
\end{minipage} 
\end{document}  \documentclass[]{article}